Think deep for reef resilience

### 2025-08-17 paper/paper_draft.qmd
auto-format
Plus minor tweak to figure caption

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef depth and the
number of years cover exceeds the carbonate budget threshold. Point colour represents the
median reef depth level in metres. Red points represent the mean number of years above a
carbonate threshold across reefs. Displays results from median time series using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
fig-align="center" width="14.82cm"}

>>>>

![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075.
The assessed carbonate budget thresholds range from 10 to 20% of total reef area. Bracketed
x-axis values represent the Spearman's correlation between reef depth and the number of
years cover exceeds the carbonate budget threshold. Point colour represents the median reef
depth in metres. Red points represent the mean number of years above an assumed carbonate
budget threshold across reefs. Note that deeper reefs are better able to maintain cover
above the indicative carbonate budget threshold. Displays results from median time series
using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
fig-align="center" width="14.82cm"}
